The normal distribution

### 2018-09-27 DATA606/Lab3/michael-normal_distribution.Rmd
Additional work on DATA 606 Lab 3

@@

    **a.** The histogram for female biiliac (pelvic) diameter (`bii.di`) belongs
    to normal probability plot letter ____.

    **b.** The histogram for female elbow diameter (`elb.di`) belongs to normal 
    probability plot letter ____.

    **c.** The histogram for general age (`age`) belongs to normal probability 
    plot letter ____.

    **d.** The histogram for female chest depth (`che.de`) belongs to normal 
    probability plot letter ____.

-   Note that normal probability plots C and D have a slight stepwise pattern.  
    Why do you think this is the case?

-   As you can see, normal probability plots can be used both to assess 
    normality and visualize skewness.  Make a normal probability plot for female 
    knee diameter (`kne.di`).  Based on this normal probability plot, is this 
    variable left skewed, symmetric, or right skewed?  Use a histogram to confirm 
    your findings.

![histQQmatch](more/histQQmatch.png)

>>>>

    ```{r echo=FALSE}
    fwgtmean <- mean(fdims$wgt)
    fwgtsd   <- sd(fdims$wgt)
    ```

    **1) Given the mean height of a male is `r round(mean(mdims$hgt), 0)` cm, what is the probability that a female is taller than the average male?**

    **The theoretical probability is: `r 1 - pnorm(q = mean(mdims$hgt), mean = fhgtmean, sd = fhgtsd)`**

    **The emperical probability is: `r sum(fdims$hgt > mean(mdims$hgt)) / length(fdims$hgt)`**

    **2) Given that the mean weight of a male is `r round(mean(mdims$wgt), 0)` kg, what is the probability that a female is heavier than the average male?**

    **The theoretical probability is: `r 1 - pnorm(q = mean(mdims$wgt), mean = fwgtmean, sd = fwgtsd)`**

    **The emperical probability is: `r sum(fdims$wgt > mean(mdims$wgt)) / length(fdims$wgt)`**

@@

    **a.** The histogram for female biiliac (pelvic) diameter (`bii.di`) belongs
    to normal probability plot letter **B**.

    **b.** The histogram for female elbow diameter (`elb.di`) belongs to normal 
    probability plot letter **C**.

    **c.** The histogram for general age (`age`) belongs to normal probability 
    plot letter **D**.

    **d.** The histogram for female chest depth (`che.de`) belongs to normal 
    probability plot letter **A**.

-   Note that normal probability plots C and D have a slight stepwise pattern.  
    Why do you think this is the case?  **Because they are variable with discrete units not continuous.  Thats what gives them the stepwise pattern.**

-   As you can see, normal probability plots can be used both to assess 
    normality and visualize skewness.  Make a normal probability plot for female 
    knee diameter (`kne.di`).  Based on this normal probability plot, is this 
    variable left skewed, symmetric, or right skewed?  Use a histogram to confirm 
    your findings.
    ```{r}
    qqnorm(fdims$kne.di)
    qqline(fdims$kne.di)
    ```

    **It is right skewed.**

    ```{r}
    hist(fdims$kne.di)
    ```

![](more/histQQmatch.png)
